### 2016-01-15 paper.tex
Add lambda symbol

The performance of cross-flow MHK turbines thus depends on both Reynolds number
and solidity (note that these issues are related, since an average blade chord
Reynolds number, $Re_{c,\mathrm{avg}} \approx \lambda U_\infty c/ \nu$, can be
expressed in terms of tip speed ratio, the optimal value of which is a function
of solidity). If numerical models are validated with physical model data that
was obtained at insufficiently high Reynolds numbers, it cannot be determined
whether problems with model predictions are caused by Reynolds number effects,
issues related to higher solidity, or both. It is uncertain whether numerical
models validated with physical model data obtained at low Reynolds number should
be considered validated at all, since the scale at which the model will be
applied is orders of magnitude larger. One way to overcome this uncertainty is
to show that the scaled physical model test has become Reynolds number
independent, and therefore validation efforts should be relevant at full-scale.

>>>>

The performance of cross-flow MHK turbines thus depends on both Reynolds number
and solidity (note that these issues are related, since an average blade chord
Reynolds number, $Re_{c,\mathrm{avg}} \approx \lambda U_\infty c/ \nu$, can be
expressed in terms of tip speed ratio $\lambda$, the optimal value of which is a
function of solidity). If numerical models are validated with physical model
data that was obtained at insufficiently high Reynolds numbers, it cannot be
determined whether problems with model predictions are caused by Reynolds number
effects, issues related to higher solidity, or both. It is uncertain whether
numerical models validated with physical model data obtained at low Reynolds
number should be considered validated at all, since the scale at which the model
will be applied is orders of magnitude larger. One way to overcome this
uncertainty is to show that the scaled physical model test has become Reynolds
number independent, and therefore validation efforts should be relevant at
full-scale.
